TODO (re-replication) (student) (cumulative science) (failure to replicate) 

### 2024-02-22 manuscript/manuscript.Rmd
poking

---
title: "TODO (re-replication) (student) (cumulative science) (failure to replicate) "
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: TODO
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: vancouver.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

## Pre-registration
Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects (CHECK IF TRUE). Each project was also individually pre-registered by the student conducting it. The overall analysis is at LINK, individual pre-registrations are linked from LINK.

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex") |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
#cors

@@

Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered). Likely driven by the two rescues discussed above, metrics related to original replication size were some of the strongest correlates of rescue replication success.

This is correlational, and we know that small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.

Two factors that seem like they would matter are relative sample size and replication closeness (using the classification scheme in @lebel), which are shown in TABLE TODO.

```{r}
parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))  |>kable_classic()

@@

TODO some of the error bars here don't look entirely consistent?

>>>>

---
title: "TODO (re-replication) (student) (cumulative science) (failure to replicate) "
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: TODO
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: apa6.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

## Pre-registration
Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects. Each project was also individually pre-registered by the student conducting it. The overall analysis is at LINK, individual pre-registrations are linked from LINK.

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="TODO CAPTION")

@@

Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered). 
While not signficant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.

Small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.

Two measures associated with how satisfying a replication attempt was are its sample size (relative to the original) and how close the replication was to the original. We show these measures (using the classification scheme of @lebel for closeness) in TABLE TODO.

```{r}
parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="TODOCAPTION", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))

@@
